Computer Assisted Verbal Autopsy: Comparing Large Language Models to Physicians for Assigning Causes to 6939 Deaths in Sierra Leone from 2019-2022

### 2025-06-26 archive/latex-2025-06-25/manuscript.tex
Archive latex and use docx instead

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-methods-brief.pdf}
\caption{Study methods.}\label{fig-methods-brief}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-csmf.pdf}
\caption{Overall model performance.}\label{fig-pccc-csmf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc.pdf}
\caption{Model performance by age group.}\label{fig-pccc}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-age.pdf}
\caption{Model performance by age range.}\label{fig-pccc-age}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{../figures/fig-pccc-cod-adult.pdf}
\caption{Model performance for adult records by COD.}\label{fig-pccc-cod-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-cod-child.pdf}
\caption{Model performance for child records by COD.}\label{fig-pccc-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{../figures/fig-pccc-cod-neo.pdf}
\caption{Model performance for neonatal records by COD.}\label{fig-pccc-cod-neo}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{../figures/fig-discuss-phyassist.pdf}
    \caption{Model suggestions integrated in the physician assignment process.}\label{fig-discuss-phyassist}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{../figures/fig-methods.pdf}
\caption{Detailed study methods.}\label{fig-methods}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.75\textwidth]{../figures/fig-map.pdf}
\caption{Study data sampling areas.}\label{fig-map}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/fig-methods-brief.pdf}
\caption{Study methods.}\label{fig-methods-brief}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/fig-pccc-csmf.pdf}
\caption{Overall model performance.}\label{fig-pccc-csmf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/fig-pccc.pdf}
\caption{Model performance by age group.}\label{fig-pccc}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/fig-pccc-age.pdf}
\caption{Model performance by age range.}\label{fig-pccc-age}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.9\textwidth]{figures/fig-pccc-cod-adult.pdf}
\caption{Model performance for adult records by COD.}\label{fig-pccc-cod-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/fig-pccc-cod-child.pdf}
\caption{Model performance for child records by COD.}\label{fig-pccc-cod-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{figures/fig-pccc-cod-neo.pdf}
\caption{Model performance for neonatal records by COD.}\label{fig-pccc-cod-neo}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{figures/fig-discuss-phyassist.pdf}
    \caption{Model suggestions integrated in the physician assignment process.}\label{fig-discuss-phyassist}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=.7\textwidth]{figures/fig-methods.pdf}
\caption{Detailed study methods.}\label{fig-methods}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.75\textwidth]{figures/fig-map.pdf}
\caption{Study data sampling areas.}\label{fig-map}
\end{figure}
